DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
small edits

\begin{abstract}
Selecting the right convolution for a spherical neural network is a delicate trade-off between its efficiency and its exactictude with respect of equivariance. DeepSphere, as a graph based method strikes as a controllable balance between these two aspects. This contribution 1) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and 2) evaluates its performance on a large set of relevant problems.
Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.

@@

DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
% An example architecture is shown in \figref{architecture}.
The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
We use the graph CNN formulation introduced in \citep{defferrard2016graphnn}, and a pooling strategy that exploits hierarchical pixelizations of the sphere.

@@

\paragraph{Graph.}
From $\V$, we construct a weighted undirected graph $\G = (\V, w)$, where the elements of $\V$ are the vertices and the weight $w_{ij} = w_{ji}$ is a similarity measure between vertices $x_i$ and $x_j$.
The combinatorial graph Laplacian $\b{L} \in \R^{n \times n}$ is defined as $\b{L} = \b{D} - \b{A}$, where $\b{A} = (w_{ij})$ is the weighted adjacency matrix, $\b{D} = (d_{ii})$ is the diagonal degree matrix, and $d_{ii} = \sum_j w_{ij}$ is the weighted degree of vertex $x_i$.
%$\b{D} = \diag(\b{A} \b{1})$
Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the only freedom in constructing $\G$ is in setting $w$.
\Secref{equivariance} shows how to set $w$ to minimize the equivariance error.
%building a good graph amounts to set a good $w$.

>>>>

\begin{abstract}
Selecting the right convolution for a spherical neural network is a delicate tradeoff between its efficiency and its exactictude with respect of equivariance. DeepSphere, as a graph based method strikes as a controllable balance between these two aspects. This contribution 1) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and 2) evaluates its performance on a large set of relevant problems.
Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.

@@

DeepSphere leverages graph convolutions to achieve the following properties: (i) computational efficiency, (ii) sampling flexibility, and (iii) rotation equivariance (\secref{equivariance}).
% An example architecture is shown in \figref{architecture}.
The main idea is to model the discretized sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
We use the graph CNN formulation introduced in \citep{defferrard2016graphnn} and a pooling strategy that exploits hierarchical pixelizations of the sphere.

@@

\paragraph{Graph.}
From $\V$, we construct a weighted undirected graph $\G = (\V, w)$, where the elements of $\V$ are the vertices and the weight $w_{ij} = w_{ji}$ is a similarity measure between vertices $x_i$ and $x_j$.
The combinatorial graph Laplacian $\b{L} \in \R^{n \times n}$ is defined as $\b{L} = \b{D} - \b{A}$, where $\b{A} = (w_{ij})$ is the weighted adjacency matrix, $\b{D} = (d_{ii})$ is the diagonal degree matrix, and $d_{ii} = \sum_j w_{ij}$ is the weighted degree of vertex $x_i$.
%$\b{D} = \diag(\b{A} \b{1})$
Given a sampling scheme $\V$, usually fixed by the application or the available measurements, the freedom in constructing $\G$ is in setting $w$.
\Secref{equivariance} shows how to set $w$ to minimize the equivariance error.
%building a good graph amounts to set a good $w$.
